Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-11 popl24/intro.tex
checkpoint

On its surface, security for MPC protocols seems similar to
probabilistic noninterference. However, MPC security differs from
noninterference in a subtle but fundamental way, and approaches for
verifying noninterference cannot naturally extend to MPC security. Our
goal is to explore and establish connections between the security
model of MPC-- the \emph{real/ideal} aka \emph{simulator security}
model -- and trace-based hyperproperties, and to leverage these
connections to obtain automated enforcement mechanisms for MPC
protocol development. Currently, proof methods for MPC protocol
development are well-studied \cite{Lindell2017} but manual and thus
tedious and error-prone, and are also non-standardized and unfamiliar
to most PL theorists. Therefore our exploration will make both
theoretical and practical contributions by bridging a gap between
information flow and simulator security methodologies.

@@

\subsection{Related Work}

We distinguish between \emph{extensional} vs.~\emph{intensional}
properties and analysis of MPC protocols. By extensional, we mean
simulator security itself as well as analysis concerned with the use
and interaction of complete secure protocols. By intensional, we mean
analysis and inner workings of protocols themselves. While the
probabilistic formulations we develop could conceivably be used
extensionally, our main focus is on automated and semi-automated
reasoning about intensional properties of protocols, both through
whole-program analysis and compositional properties of program
components that support security.

@@

In the realm of intensional analysis, previous work has shown how to
reduce proofs of simulator security to program equivalence assertions,
which supports the application of known techniques in automated verification
\cite{8429300}. However, they focus on noninterference properties,
which are arguably sound but notably incomplete wrt MPC functionality
as we discuss above and in Section
\ref{section-hyperprop-ni}. Probabilistic Separation Logic
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence in programs.  They consider
several MPC protocols and show how to systematically deduce, e.g.,
probabilistic independence of input secrets and adversarial views that
are critical intensional properties of simulator security.  However,
their focus on independence does not address the subtleties of
dependence that arise during MPC protocol execution, and the authors
do not formulate or prove simulator security properties in
\cite{barthe2019probabilistic}. The $\lambda_{\mathrm{obliv}}$
language \cite{darais2019language} is perhaps most closely related to
our work. Here, a type system is used to automatically enforce
so-called probabilistic trace obliviousness and they show how to use
their system to implement several variants of oblivious RAM. However,
obliviousness is related to noninterference and does not address
allowable information leakage as in MPC, and their use of type
linearity disallows the reuse of sampled probabilistic values which is
common in the MPC idiom, as our examples will illustrate. Similarly,
previous work on oblivious data structures \cite{10.1145/3498713},
while intended for sound integration into MPC protocols, focus on
expression and enforcement of obliviousness and do not account
for allowable information leakage.

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we then formulate a novel hyperproperty of program execution
traces, called \emph{noninterference modulo output ($\NIMO$)} that we
demonstrate implies passive simulator security.

>>>>

On its surface, security for MPC protocols seems similar to
probabilistic noninterference. However, MPC security differs from
noninterference in a subtle but fundamental way, and approaches for
verifying noninterference cannot naturally extend to MPC security. Our
goal is to explore connections between the security model of MPC-- the
\emph{real/ideal} aka \emph{simulator security} model -- and
trace-based hyperproperties, and to leverage these connections to
obtain automated enforcement mechanisms for MPC protocol
development. Currently, proof methods for MPC protocol development are
well-studied \cite{Lindell2017} with some previous work leveraging
connections with hyperproperties \cite{8429300}. But these methods
require fully manual proof construction and are thus tedious and
error-prone. Therefore our exploration makes both theoretical and
practical contributions.

@@

We distinguish between \emph{extensional} vs.~\emph{intensional}
properties and analysis of MPC protocols. By extensional, we mean
simulator security itself as well as analysis concerned with the use
and interaction of complete secure protocols. By intensional, we mean
analysis and inner workings of protocols themselves

\paragraph{Hyperproperty formulation.} In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we can then formulate extensional hyperproperties, including
\emph{noninterference modulo output ($\NIMO$)} that implies passive
simulator security. But further, we can formulate intensional
protocol properties such as probabilistic conditioning of program
distributions.

\subsection{Related Work}
\label{section-related-work}

Our main focus is on automated and semi-automated reasoning about
intensional properties of protocols, both through whole-program
analysis and compositional properties of program components that
support security.

@@

In the realm of intensional analysis, previous work has shown how to
reduce proofs of simulator security to program equivalence assertions,
which supports computer-aided verification of MPC protocols in
EasyCrypt \cite{8429300}. This work also leveraged hyperproperty
characterizations of simulator security, both passive and
active. However, their EasyCrpyt security proof constructions are
entirely manual. Probabilistic Separation Logic
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence in programs.  They consider
several MPC protocols and show how to systematically deduce, e.g.,
probabilistic independence of input secrets and adversarial views that
are critical intensional properties of simulator security.  However,
their focus on independence does not address the subtleties of
dependence that arise during MPC protocol execution, and the authors
do not formulate or prove simulator security properties in
\cite{barthe2019probabilistic}. The $\lambda_{\mathrm{obliv}}$
language \cite{darais2019language} is perhaps most closely related to
our work. Here, a type system is used to automatically enforce
so-called probabilistic trace obliviousness and they show how to use
their system to implement several variants of oblivious RAM. However,
obliviousness is related to noninterference and does not address
allowable information leakage as in MPC, and their use of type
linearity disallows the reuse of sampled probabilistic values which is
common in the MPC idiom, as our examples will illustrate. Similarly,
previous work on oblivious data structures \cite{10.1145/3498713},
while intended for sound integration into MPC protocols, focus on
expression and enforcement of obliviousness and do not account for
allowable information leakage.

@@

### 2023-07-11 popl24/main.tex
checkpoint

\begin{abstract}
Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern distributed applications. Security for MPC protocols
is superficially similar to probabilistic noninterference, but differs
in a subtle but fundamental way, and approaches for verifying
noninterference cannot naturally extend to MPC security.  Currently,
proof methods for MPC protocols are well-studied but manual
and thus tedious and error-prone, and are also non-standardized and
unfamiliar to most PL theorists.  Our goal is to strengthen
connections between the security model of MPC and trace-based
hyperproperties, and to leverage them to obtain automated
enforcement mechanisms for MPC protocol development.  We define a
novel hyperproperty that is provably sound for MPC security, as a
foundation for fully and partially automated verification of passive
MPC security in protocols including arbitrarily large YGC and GMW
circuits.
\end{abstract}

@@

>>>>

\begin{abstract}
Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern distributed applications. Security for MPC protocols
is superficially similar to probabilistic noninterference, but differs
in a subtle but fundamental way, and approaches for verifying
noninterference cannot naturally extend to MPC security.  Currently,
proof methods for MPC protocols are well-studied but manual and thus
tedious and error-prone, and are also non-standardized and unfamiliar
to most PL theorists.  Our goal is to leverage connections between the
security model of MPC and trace-based hyperproperties to obtain
automated proof methods for MPC protocol development.  We develop a
language model with a tightly coupled notion of probabilistic program
distributions, as a foundation for fully and partially automated
verification of passive MPC security in protocols including
arbitrarily large YGC and GMW circuits.
\end{abstract}

@@

\input{examples}

%\input{types}
